### 2019-08-05 tables/03_model_summary.Rmd
build global re results table

dt           <- r2_re
dt$elpd_diff <- loo_re$elpd_diff
dt <- dplyr::select(dt, 
                    response, term, r2 = Estimate, elpd_diff)
test <- dt[order(dt$response, dt$elpd_diff, decreasing = TRUE),]

options(knitr.kable.NA = "-")  
dplyr::filter(dt, str_detect(Model, "tp")) %>%
  dplyr::select(-Model) %>%
  dplyr::rename("$R^2$" = Estimate) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

\pagebreak
```{r tn_results}
dplyr::filter(dt, str_detect(Model, "tn")) %>%
  dplyr::select(-Model) %>%
  dplyr::rename("$R^2$" = Estimate) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")
```

>>>>

dt           <- r2_re
dt$elpd_diff <- loo_re$elpd_diff
dt <- dplyr::select(dt, 
                    response, term, r2 = Estimate, elpd_diff)
dt <- dt[order(dt$response, dt$elpd_diff, decreasing = FALSE),]

options(knitr.kable.NA = "-")  
dplyr::filter(dt, str_detect(response, "tp")) %>%
  dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

\pagebreak
```{r tn_results}
dplyr::filter(dt, str_detect(response, "tn")) %>%
  dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")
```
